Sparse spectral and $p$-finite element methods on disk-slices and trapeziums I: zero boundary conditions

### 2019-04-03 papers/halfdisk/halfdisk.tex
Added more refs to eqns

We can generalise this for our purposes in the following proposition.
\begin{proposition}
Let
\begin{align*}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align*}
with $\rho : (\alpha, \beta) \to \R$. Further, let $w^{(a,b,c)}_H(x)$ and $w^{(a,b)}_P(x)$ be two weight functions on the intervals $(\alpha, \beta)$ and $(\gamma, \delta)$ respectively, given by:
\begin{align}
\begin{cases}
w^{(a,b,c)}_H(x) &:= (\beta - x)^a \: (x - \alpha)^{b} \: \rho(x)^{c} \\
w^{(a,b)}_P(x) &:= (\delta-x)^a \: (x - \gamma)^b
\end{cases}
\end{align}
where the three-parameter family of orthogonal polynomials on $[\alpha,\beta]$ given by $\{H_n^{(a,b,c)}\}$ are orthogonal with respect to $w^{(a,b,c)}_H(x)$, and the two-parameter family of orthogonal polynomials on $[\gamma,\delta]$ given by $\{P_n^{(a,b)}\}$ are orthogonal with respect to $w^{(a,b)}_P(x)$.

@@

For the half disk, the weight $W^{(a,b)}(x,y) = x^a \: (1-x^2-y^2)^b$ results from setting:
\begin{align}
\begin{cases}
(\alpha,\beta) &:= (0.1) \\
(\gamma,\delta) &:= (-1,1) \\
\rho(x) &:= (1-x^2)^{\half} \\
w_1(x) &:= w_H^{(a,b)}(x) := x^a \: (1-x^2)^b \\
w_2(x) &:= w_P^{(b)}(x) := (1-x^2)^b = (1-x)^b \: (1+x)^b,
\end{cases}
\end{align}
Note here the we have made the adjustment that $w^{(a,b,c)}_H(x) = (\beta - x)^a \: (x - \alpha)^{b} \: \rho(x)^{2c}$ and simply set the first parameter to zero and removed it for the specific half-disk case. This is for ease of writing and computation, by ensuring we reduce the need to incorporate unnecessary parameters and instead yield a two-parameter family of 2D orthogonal polynomials.

@@

We can express the three-term recurrences associated to $H_n^{(a,b)}$ and $P_n^{(b,b)}$ as
\begin{align}
x H_n^{(a,b)}(x) &= \beta_n^{(a,b)} H_{n+1}^{(a,b)}(x) + \alpha_n^{(a,b)} H_n^{(a,b)}(x) + \beta_{n-1}^{(a,b)} H_{n-1}^{(a,b)}(x) \\
y P_n^{(b,b)}(y) &= \delta_n^{(b)} P_{n+1}^{(b,b)}(y) + \gamma_n^{(b)} P_n^{(b,b)}(y) + \delta_{n-1}^{(b)} P_{n-1}^{(b,b)}(y),
\end{align}
where we note that \(\gamma_n^{(b)} = 0\), for \( n = 0,1,2,\dots\). We can use these to determine the 2D recurences for $P_{n,k}^{(a,b)}(x,y)$:

@@

Three-term recurrences lead to Jacobi operators that correspond to multiplication by $x$ and $y$. Define, for $n=0,1,2,\dots$: 
\begin{align}
\bigPab_n := \begin{pmatrix}
		P^{(a,b)}_{n,-n}(x,y) \\
		\vdots \\
		P^{(a,b)}_{n,n}(x,y)
	\end{pmatrix} \in \R^{n+1}, 
\quad \quad 
\bigPab := \begin{pmatrix}
		\bigPab_0 \\
		\bigPab_1 \\
		\bigPab_2 \\
		\vdots \\
	\end{pmatrix}
\end{align}
and set $J_x^{(a,b)}, J_y^{(a,b)}$ as the Jacobi matrices corresponding to
\begin{align}
J_x^{(a,b)} \: \bigPab(x,y) = x \: \bigPab(x,y), \quad J_y^{(a,b)} \: \bigPab(x,y) = y \: \bigPab(x,y).
\end{align}
Then $J_x^{(a,b)}, J_y^{(a,b)}$ have the Banded-Block-Banded structures
\begin{align}
J_{x/y}^{(a,b)} &= \begin{pmatrix}
		B^{x/y}_0 & A^{x/y}_0 & & & & \\
		C^{x/y}_1 & B^{x/y}_1 & A^{x/y}_1 & & & \\
		& C^{x/y}_2 & B^{x/y}_2 & A^{x/y}_2  & & & \\
		& & C^{x/y}_3 & \ddots & \ddots & \\
		& & & \ddots & \ddots & \ddots \\
	\end{pmatrix}
\end{align}
where
\begin{align}
A^x_n &:= \begin{pmatrix}
		\alphaab_{n+1,0,1} & 0 & \hdots & 0 \\
		& \ddots & & \vdots & \\
		& & \alphaab_{n+1,n,1} & 0 \\
	    \end{pmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots \\
B^x_n &:= \begin{pmatrix}
		\alphaab_{n,0,2} & & \\
		& \ddots & \\
		& & \alphaab_{n,n,2} \\
	    \end{pmatrix} \in \R^{(n+1)\times(n+1)} \quad n = 0,1,2,\dots \\
C^x_n &:= \big( A^x_n \big)^T \in \R^{(n+1)\times n},  \quad n = 1,2,\dots \\ 
\nonumber \\
A^y_n &:= \begin{pmatrix}
		0 & \betaab_{n,0,6} & & & \\
		\betaab_{n,1,5} & 0 & & & \\
		& \ddots & \ddots & \ddots & \\
		& & \betaab_{n,n,5}& 0 & \betaab_{n,n,6} \\
	    \end{pmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots \\
B^y_n &:= \begin{pmatrix}
		0 & \betaab_{n,0,4} & & \\
		\betaab_{n,1,3} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-1,4} \\
		& & \betaab_{n,n,3} & 0
	    \end{pmatrix} \in \R^{(n+1)\times(n+1)}  \quad n = 0,1,2,\dots \\
C^y_n &:= \begin{pmatrix}
		0 & \betaab_{n,0,2} & & \\
		\betaab_{n,1,1} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-2,2} \\
		& & \ddots & 0 \\
		& & & \betaab_{n,n,1} \\
	    \end{pmatrix} \in \R^{(n+1)\times n}, \quad n = 1,2,\dots
\end{align}

@@

Combining each system in (71) we can write the block-tridiagonal system
\begin{align}
\renewcommand\arraystretch{1.3}
\mleft[
\begin{array}{cccc}
		1 & & & \\
		B_0-G_0(x,y) & A_0 & & \\
		C_1 & B_1-G_1(x,y) & \quad A_1 \quad & \\
		& C_2 & \ddots & \ddots \\
		& & \ddots &
\end{array}
\mright]
\bigPab(x,y)
=
\begin{pmatrix}
	P^{(a,b)}_{0,0} \\ 0 \\ 0 \\ \vdots \\ 0 \\
\end{pmatrix}.
\end{align}
where we note \(P^{(a,b)}_{0,0}(x,y) \equiv H_0^{(a,b)} \: P_0^{(b,b)}\), and for each $n = 0,1,2\dots$:
\begin{align}
A_n &:= \begin{pmatrix}
		A^x_n \\
		A^y_n \\
		A^z_n
	    \end{pmatrix} \in \R^{2(n+1)\times(n+3)} \quad (n \ne N), \quad
C_n := \begin{pmatrix}
		C^x_n \\
		C^y_n
	    \end{pmatrix} \in \R^{2(n+1)\times n} \quad (n \ne 0), \nonumber \\
B_n &:= \begin{pmatrix}
		B^x_n \\
		B^y_n
	    \end{pmatrix} \in \R^{2(n+1)\times(n+1)}, \quad
G_n(x,y) := \begin{pmatrix}
		xI_{n+1} \\
		yI_{n+1}
	    \end{pmatrix} \in \R^{2(n+1)\times(n+1)}.
\end{align}

@@

To obtain the recurrence coefficients for the $\{H_n^{(a,b)}\}$ OPs in (4), we use a version of the Stieltjes algorithm. Recall that
\begin{align}
x H_n^{(a,b)}(x) &= \beta_n^{(a,b)} H_{n+1}^{(a,b)}(x) + \alpha_n^{(a,b)} H_n^{(a,b)}(x) + \beta_{n-1}^{(a,b)} H_{n-1}^{(a,b)}(x), \quad n = 0,1,2,\dots
\end{align}
where we define $\beta_{-1}^{(a,b)} = 0$ and $H_{-1}^{(a,b)}(x) \equiv 0$.

@@

We seek $u_h \in V_h$ s.t.
\begin{align}
	L(v_h) = a(u_h,v_h) \quad \forall \: v_h \in V_h.
\end{align}

Define $\Lambda^{(a,b)} := \langle \bigP^{(a,b)}, \: {\bigP^{(a,b)}}^T \rangle_{W^{(a,b)}}$ where $W^{(a,b)}$ is the weight with which the OPs in $\bigP^{(a,b)}$ are orthogonal with respect to. Note that due to orthogonality this is a diagonal matrix. We can choose a basis for $V_h$ by using the weighted orthogonal polynomials on $\element$ with parameters $a = b = 1$:
\begin{align}
\bigWii(x,y) &:= \begin{pmatrix}
		\bigWii_0(x,y) \\
		\bigWii_1(x,y) \\
		\bigWii_2(x,y) \\
		\vdots \\
		\bigWii_p(x,y)
	\end{pmatrix}, \\
\bigWii_n(x,y) &:= \begin{pmatrix}
		\Wii(x,y) \: \Pii_{n,0}(x,y) \\
		\vdots \\
		\Wii(a,y) \: \Pii_{n,n}(x,y)
	\end{pmatrix} \in \R^{n+1} \quad \forall n = 0,1,2,\dots,p,
\end{align}
and rewrite (73) in matrix form:
\begin{align}
	a(u_h,v_h) &= \int_\element \nabla u_h \cdot \nabla v_h \: d\mathbf{x} \\
	&= \int_\element \begin{pmatrix}
					\partial_x v_h \\
					\partial_y v_h
				\end{pmatrix}^T 
				\begin{pmatrix}
					\partial_x u_h \\
					\partial_y u_h
				\end{pmatrix}
				\\
	&= \int_\element \begin{pmatrix}
					\bigPoo^T \Wii_x \mathbf{v} \\
					\bigPoo^T T^{(1,0)\to(0,0)} \Wii_y \mathbf{v}
				\end{pmatrix}^T 
				\begin{pmatrix}
					\bigPoo^T \Wii_x \mathbf{u} \\
					\bigPoo^T T^{(1,0)\to(0,0)} \Wii_y \mathbf{u}
				\end{pmatrix}
				\\
	&= \int_\element \Big( \mathbf{v}^T {\Wii_x}^T \bigPoo \bigPoo^T \Wii_x \mathbf{u} \nonumber \\
					& \quad \quad \quad + \mathbf{v}^T ({T^{(1,0)\to(0,0)} \Wii_y})^T \bigPoo \bigPoo^T T^{(1,0)\to(0,0)} \Wii_y \mathbf{u}  \Big) \: d\mathbf{x} \\
	&= \mathbf{v}^T \: \Big( {\Wii_x}^T \Lambda^{(0,0)} \Wii_x + ({T^{(1,0)\to(0,0)} \Wii_y})^T \Lambda^{(0,0)} T^{(1,0)\to(0,0)} \Wii_y \Big) \: \mathbf{u}
\end{align}
where $\mathbf{u}, \mathbf{v}$ are the coefficient vectors of the expansions of $u_h, v_h \in V_h$ respectively in the $V_h$ basis ($\bigWii$ OPs), and
\begin{align}
	L(v_h) &= \int_\element \: v_h \: f \: d\mathbf{x} \\
	&= \int_\element \: \mathbf{v}^T \: \bigWii \: \bigPii^T \: \mathbf{f} \: d\mathbf{x} \\
	&= \mathbf{v}^T \: \langle \bigPii, {\bigPii}^T \rangle_{\Wii} \: d\mathbf{x} \\
	&= \mathbf{v}^T \Lambda^{(1,1)} \: \mathbf{f},
\end{align}
where $\mathbf{f}$ is the coefficient vector for the expansion of the function $f(x,y)$ in the $\bigPii$ OP basis.

Since (73) is equivalent to stating that
\begin{align}
	L(\Wii \Pii_{n,k}) = a(u_h,\Wii \Pii_{n,k}) \quad \forall \: n = 0,\dots,p, \: k = 0,\dots,n,
\end{align}
(i.e. holds for all basis functions of $V_h$) by choosing $v_h$ as each basis function, we can equivalently write the linear system for our finite element problem as:
\begin{align}
A\mathbf{u} = \tilde{\mathbf{f}}.
\end{align}
where the (element) stiffness matrix $A$ is defined by 
\begin{align}
A = {\Wii_x}^T \Lambda^{(0,0)} \Wii_x + ({T^{(1,0)\to(0,0)} \Wii_y})^T \Lambda^{(0,0)} T^{(1,0)\to(0,0)} \Wii_y, 
\end{align}
and the load vector $\tilde{\mathbf{f}}$ is given by 
\begin{align}
\tilde{\mathbf{f}} = \Lambda^{(1,1)} \: \mathbf{f}.
\end{align}

>>>>

We can generalise this for our purposes in the following proposition. \bstodoinline{I have added in this proposition to explain how I think this generalises to the main domain shapes we are thinking about, including your triangle case.}
\begin{proposition}
Let
\begin{align*}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align*}
with $\rho : (\alpha, \beta) \to \R$. Further, let $w^{(a,b,c)}_H(x)$ and $w^{(a,b)}_P(x)$ be two weight functions on the intervals $(\alpha, \beta)$ and $(\gamma, \delta)$ respectively, given by:
\begin{align}
\begin{cases}
w^{(a,b,c)}_H(x) &:= (\beta - x)^a \: (x - \alpha)^{b} \: \rho(x)^{c} \\
w^{(a,b)}_P(x) &:= (\delta-x)^a \: (x - \gamma)^b
\end{cases}
\end{align}
where the three-parameter family of orthogonal polynomials on $[\alpha,\beta]$ given by $\{H_n^{(a,b,c)}\}$ are orthogonal with respect to $w^{(a,b,c)}_H(x)$, and the two-parameter family of orthogonal polynomials on $[\gamma,\delta]$ given by $\{P_n^{(a,b)}\}$ are orthogonal with respect to $w^{(a,b)}_P(x)$.

@@

For the half disk, the weight $W^{(a,b)}(x,y) = x^a \: (1-x^2-y^2)^b$ results from setting:
\begin{align}
\begin{cases}
(\alpha,\beta) &:= (0.1) \\
(\gamma,\delta) &:= (-1,1) \\
\rho(x) &:= (1-x^2)^{\half} \\
w_1(x) &:= w_H^{(a,b)}(x) := x^a \: (1-x^2)^b \\
w_2(x) &:= w_P^{(b)}(x) := (1-x^2)^b = (1-x)^b \: (1+x)^b,
\end{cases}
\end{align}
\bstodoinline{Hope the following makes sense. The generalisation I have, and how I originally wrote/coded up the half-disk case use slightly different conventions regarding the parameters - would it be worth reframing the paper to match this generalisation, or is this fine?}
Note here the we have made the adjustment that $w^{(a,b,c)}_H(x) = (\beta - x)^a \: (x - \alpha)^{b} \: \rho(x)^{2c}$ and simply set the first parameter to zero and removed it for the specific half-disk case. This is for ease of writing and computation, by ensuring we reduce the need to incorporate unnecessary parameters and instead yield a two-parameter family of 2D orthogonal polynomials.

@@

We can express the three-term recurrences associated to $H_n^{(a,b)}$ and $P_n^{(b,b)}$ as
\begin{align}
x H_n^{(a,b)}(x) &= \beta_n^{(a,b)} H_{n+1}^{(a,b)}(x) + \alpha_n^{(a,b)} H_n^{(a,b)}(x) + \beta_{n-1}^{(a,b)} H_{n-1}^{(a,b)}(x) 
\label{eqn:Hrecurrence} \\
y P_n^{(b,b)}(y) &= \delta_n^{(b)} P_{n+1}^{(b,b)}(y) + \gamma_n^{(b)} P_n^{(b,b)}(y) + \delta_{n-1}^{(b)} P_{n-1}^{(b,b)}(y),
\end{align}
where we note that \(\gamma_n^{(b)} = 0\), for \( n = 0,1,2,\dots\). We can use these to determine the 2D recurences for $P_{n,k}^{(a,b)}(x,y)$:

@@

Three-term recurrences lead to Jacobi operators that correspond to multiplication by $x$ and $y$. Define, for $n=0,1,2,\dots$: 
\begin{align}
\bigPab_n := \begin{pmatrix}
		P^{(a,b)}_{n,-n}(x,y) \\
		\vdots \\
		P^{(a,b)}_{n,n}(x,y)
	\end{pmatrix} \in \R^{n+1}, 
\quad \quad 
\bigPab := \begin{pmatrix}
		\bigPab_0 \\
		\bigPab_1 \\
		\bigPab_2 \\
		\vdots \\
	\end{pmatrix}
\end{align}
and set $J_x^{(a,b)}, J_y^{(a,b)}$ as the Jacobi matrices corresponding to
\begin{align}
J_x^{(a,b)} \: \bigPab(x,y) = x \: \bigPab(x,y), \quad J_y^{(a,b)} \: \bigPab(x,y) = y \: \bigPab(x,y).
\label{eqn:jacobimatricesdefinition}
\end{align}
Then $J_x^{(a,b)}, J_y^{(a,b)}$ have the Banded-Block-Banded structures
\begin{align}
J_{x/y}^{(a,b)} &= \begin{pmatrix}
		B^{x/y}_0 & A^{x/y}_0 & & & & \\
		C^{x/y}_1 & B^{x/y}_1 & A^{x/y}_1 & & & \\
		& C^{x/y}_2 & B^{x/y}_2 & A^{x/y}_2  & & & \\
		& & C^{x/y}_3 & \ddots & \ddots & \\
		& & & \ddots & \ddots & \ddots \\
	\end{pmatrix}
\end{align}
where
\begin{align}
A^x_n &:= \begin{pmatrix}
		\alphaab_{n+1,0,1} & 0 & \hdots & 0 \\
		& \ddots & & \vdots & \\
		& & \alphaab_{n+1,n,1} & 0 \\
	    \end{pmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots \\
B^x_n &:= \begin{pmatrix}
		\alphaab_{n,0,2} & & \\
		& \ddots & \\
		& & \alphaab_{n,n,2} \\
	    \end{pmatrix} \in \R^{(n+1)\times(n+1)} \quad n = 0,1,2,\dots \\
C^x_n &:= \big( A^x_n \big)^T \in \R^{(n+1)\times n},  \quad n = 1,2,\dots \\ 
\nonumber \\
A^y_n &:= \begin{pmatrix}
		0 & \betaab_{n,0,6} & & & \\
		\betaab_{n,1,5} & 0 & & & \\
		& \ddots & \ddots & \ddots & \\
		& & \betaab_{n,n,5}& 0 & \betaab_{n,n,6} \\
	    \end{pmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots \\
B^y_n &:= \begin{pmatrix}
		0 & \betaab_{n,0,4} & & \\
		\betaab_{n,1,3} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-1,4} \\
		& & \betaab_{n,n,3} & 0
	    \end{pmatrix} \in \R^{(n+1)\times(n+1)}  \quad n = 0,1,2,\dots \\
C^y_n &:= \begin{pmatrix}
		0 & \betaab_{n,0,2} & & \\
		\betaab_{n,1,1} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-2,2} \\
		& & \ddots & 0 \\
		& & & \betaab_{n,n,1} \\
	    \end{pmatrix} \in \R^{(n+1)\times n}, \quad n = 1,2,\dots
\end{align}

@@

Combining each system in (\ref{eqn:jacobimatricesdefinition}) we can write the block-tridiagonal system
\begin{align}
\renewcommand\arraystretch{1.3}
\mleft[
\begin{array}{cccc}
		1 & & & \\
		B_0-G_0(x,y) & A_0 & & \\
		C_1 & B_1-G_1(x,y) & \quad A_1 \quad & \\
		& C_2 & \ddots & \ddots \\
		& & \ddots &
\end{array}
\mright]
\bigPab(x,y)
=
\begin{pmatrix}
	P^{(a,b)}_{0,0} \\ 0 \\ 0 \\ \vdots \\ 0 \\
\end{pmatrix}.
\end{align}
where we note \(P^{(a,b)}_{0,0}(x,y) \equiv H_0^{(a,b)} \: P_0^{(b,b)}\), and for each $n = 0,1,2\dots$:
\begin{align}
A_n &:= \begin{pmatrix}
		A^x_n \\
		A^y_n \\
		A^z_n
	    \end{pmatrix} \in \R^{2(n+1)\times(n+3)} \quad (n \ne N), \quad
C_n := \begin{pmatrix}
		C^x_n \\
		C^y_n
	    \end{pmatrix} \in \R^{2(n+1)\times n} \quad (n \ne 0), \nonumber \\
B_n &:= \begin{pmatrix}
		B^x_n \\
		B^y_n
	    \end{pmatrix} \in \R^{2(n+1)\times(n+1)}, \quad
G_n(x,y) := \begin{pmatrix}
		xI_{n+1} \\
		yI_{n+1}
	    \end{pmatrix} \in \R^{2(n+1)\times(n+1)}.
\end{align}

@@

To obtain the recurrence coefficients for the $\{H_n^{(a,b)}\}$ OPs in (\ref{eqn:Hrecurrence}), we use a version of the Stieltjes algorithm. Recall that
\begin{align}
x H_n^{(a,b)}(x) &= \beta_n^{(a,b)} H_{n+1}^{(a,b)}(x) + \alpha_n^{(a,b)} H_n^{(a,b)}(x) + \beta_{n-1}^{(a,b)} H_{n-1}^{(a,b)}(x), \quad n = 0,1,2,\dots
\end{align}
where we define $\beta_{-1}^{(a,b)} = 0$ and $H_{-1}^{(a,b)}(x) \equiv 0$.

@@

We seek $u_h \in V_h$ s.t.
\begin{align}
	L(v_h) = a(u_h,v_h) \quad \forall \: v_h \in V_h.
	\label{eqn:FEMweakform}
\end{align}

Define $\Lambda^{(a,b)} := \langle \bigP^{(a,b)}, \: {\bigP^{(a,b)}}^T \rangle_{W^{(a,b)}}$ where $W^{(a,b)}$ is the weight with which the OPs in $\bigP^{(a,b)}$ are orthogonal with respect to. Note that due to orthogonality this is a diagonal matrix. We can choose a basis for $V_h$ by using the weighted orthogonal polynomials on $\element$ with parameters $a = b = 1$:
\begin{align}
\bigWii(x,y) &:= \begin{pmatrix}
		\bigWii_0(x,y) \\
		\bigWii_1(x,y) \\
		\bigWii_2(x,y) \\
		\vdots \\
		\bigWii_p(x,y)
	\end{pmatrix}, \\
\bigWii_n(x,y) &:= \begin{pmatrix}
		\Wii(x,y) \: \Pii_{n,0}(x,y) \\
		\vdots \\
		\Wii(a,y) \: \Pii_{n,n}(x,y)
	\end{pmatrix} \in \R^{n+1} \quad \forall n = 0,1,2,\dots,p,
\end{align}
and rewrite (\ref{eqn:FEMweakform}) in matrix form:
\begin{align}
	a(u_h,v_h) &= \int_\element \nabla u_h \cdot \nabla v_h \: d\mathbf{x} \\
	&= \int_\element \begin{pmatrix}
					\partial_x v_h \\
					\partial_y v_h
				\end{pmatrix}^T 
				\begin{pmatrix}
					\partial_x u_h \\
					\partial_y u_h
				\end{pmatrix}
				\\
	&= \int_\element \begin{pmatrix}
					\bigPoo^T \Wii_x \mathbf{v} \\
					\bigPoo^T T^{(1,0)\to(0,0)} \Wii_y \mathbf{v}
				\end{pmatrix}^T 
				\begin{pmatrix}
					\bigPoo^T \Wii_x \mathbf{u} \\
					\bigPoo^T T^{(1,0)\to(0,0)} \Wii_y \mathbf{u}
				\end{pmatrix}
				\\
	&= \int_\element \Big( \mathbf{v}^T {\Wii_x}^T \bigPoo \bigPoo^T \Wii_x \mathbf{u} \nonumber \\
					& \quad \quad \quad + \mathbf{v}^T ({T^{(1,0)\to(0,0)} \Wii_y})^T \bigPoo \bigPoo^T T^{(1,0)\to(0,0)} \Wii_y \mathbf{u}  \Big) \: d\mathbf{x} \\
	&= \mathbf{v}^T \: \Big( {\Wii_x}^T \Lambda^{(0,0)} \Wii_x + ({T^{(1,0)\to(0,0)} \Wii_y})^T \Lambda^{(0,0)} T^{(1,0)\to(0,0)} \Wii_y \Big) \: \mathbf{u}
\end{align}
where $\mathbf{u}, \mathbf{v}$ are the coefficient vectors of the expansions of $u_h, v_h \in V_h$ respectively in the $V_h$ basis ($\bigWii$ OPs), and
\begin{align}
	L(v_h) &= \int_\element \: v_h \: f \: d\mathbf{x} \\
	&= \int_\element \: \mathbf{v}^T \: \bigWii \: \bigPii^T \: \mathbf{f} \: d\mathbf{x} \\
	&= \mathbf{v}^T \: \langle \bigPii, {\bigPii}^T \rangle_{\Wii} \: d\mathbf{x} \\
	&= \mathbf{v}^T \Lambda^{(1,1)} \: \mathbf{f},
\end{align}
where $\mathbf{f}$ is the coefficient vector for the expansion of the function $f(x,y)$ in the $\bigPii$ OP basis.

Since (\ref{eqn:FEMweakform}) is equivalent to stating that
\begin{align}
	L(\Wii \Pii_{n,k}) = a(u_h,\Wii \Pii_{n,k}) \quad \forall \: n = 0,\dots,p, \: k = 0,\dots,n,
\end{align}
(i.e. holds for all basis functions of $V_h$) by choosing $v_h$ as each basis function, we can equivalently write the linear system for our finite element problem as:
\begin{align}
A\mathbf{u} = \tilde{\mathbf{f}}.
\end{align}
where the (element) stiffness matrix $A$ is defined by 
\begin{align}
A = {\Wii_x}^T \Lambda^{(0,0)} \Wii_x + ({T^{(1,0)\to(0,0)} \Wii_y})^T \Lambda^{(0,0)} T^{(1,0)\to(0,0)} \Wii_y, 
\end{align}
and the load vector $\tilde{\mathbf{f}}$ is given by 
\begin{align}
\tilde{\mathbf{f}} = \Lambda^{(1,1)} \: \mathbf{f}.
\end{align}
